Online Laterality Battery Pre-Processing - short version

### 2020-07-20 battery-preprocessing_v6_DB.Rmd
including %correct for RDT in allsum.csv

@@

allsum$exRDT <- 0
allsum$exRDT[allsum$subject %in% exRDT]<-1 #decided best to have separate column for exclusion for each task
w<-which(allsum$exRDT==0)  
incRDT <- allsum$subject[w]
ninc <- length(incRDT)
print(paste0('RDT: number remaining after exclusions = ',ninc))
```

>>>>

#Also record % correct for each category in allsum
for (d in 1:2){
  myfile<-RDT_df1
  if(d==2){ myfile<-RDT_df2}
pcorL<-myfile[myfile$side=='left',]
pcorR<- myfile[myfile$side=='right',]
pcorNull <- myfile[myfile$side=='no rhyme',]
pcorL<-select(pcorL,subject,p.corr)
pcorR<-select(pcorR,subject,p.corr)
pcorNull<-select(pcorNull,subject,p.corr)
colnames(pcorL)[2]<-paste0('RDT',d,'.pcorrL')
colnames(pcorR)[2]<-paste0('RDT',d,'.pcorrR')
colnames(pcorNull)[2]<-paste0('RDT',d,'.pcorrNull')
allsum <- merge(allsum,pcorL,by="subject")
allsum <- merge(allsum,pcorR,by="subject")
allsum <- merge(allsum,pcorNull,by="subject")
}

@@

allsum$exRDT <- 0
allsum$exRDT[allsum$subject %in% exRDT]<-1 #decided best to have separate column for exclusion for each task
w<-which(allsum$exRDT==0)  
incRDT <- allsum$subject[w]
ninc <- length(incRDT)
print(paste0('RDT: number remaining after exclusions = ',ninc))
